---
title: "HW1 Task 6"
output: github_document
---

```{r}
library(gapminder)
library(tidyverse)
library(broom)
library(MASS)
library(listviewer)
```

## Task 6: Work with a nested data frame
```{r}
gap_nested <- gapminder %>% 
   group_by(continent, country) %>% 
   nest()

gap_nested %>% View()
```

```{r, warning=F, results='asis'}
le_vs_yr <- function(df) {
  lm(lifeExp ~ I(year - 1950), data = df)
}
rob_vs_yr <- function(df){
   rlm(lifeExp ~ I(year - 1950), data = df)
}

gap_coefs <- 
  gap_nested %>% 
   mutate(fit_ls = map(data, le_vs_yr), 
          fit_rob = map(data, rob_vs_yr)) %>% 
  mutate(tidy_ls = map(fit_ls, tidy), 
         tidy_rob = map(fit_rob, tidy)) %>%
  unnest(tidy_ls, tidy_rob) %>%
  dplyr::select(continent, country, 
                ls_term = term, ls_est = estimate, 
                rob_term = term1, rob_est = estimate1)


gap_analysis <- 
  gap_coefs %>%
  spread(key = ls_term, value = ls_est) %>%
  mutate(ls_int = lag(`(Intercept)`), 
         ls_slope = `I(year - 1950)`) %>% 
  dplyr::select(continent:rob_est, ls_int, ls_slope) %>%
  spread(key = rob_term, value = rob_est) %>%
  mutate(rob_int = lead(`(Intercept)`), 
         rob_slope = `I(year - 1950)`)  %>% 
  dplyr::select(continent:ls_slope, rob_int, rob_slope) %>%
  na.omit() %>%
  mutate(int_diff_ratio = (rob_int - ls_int)/ls_int, 
         slope_diff_ratio = (rob_slope - ls_slope)/ls_slope)


gap_analysis %>%
  arrange(desc(slope_diff_ratio)) %>%
  head(10) %>%
  knitr::kable(digits = 2, align ="r", padding = 10)
```

I compared the slope and intercept difference of two fittings: OLS and robust LS. It can be seen that Swaziland might have some interesting story because the slope difference of two fittings is as high as 120%. It can be concluded that the linear gitting might not be a good fit for the case, or there are some influential outliers (abnormal data included). 


## Report your process

Among all the questions I tried, I found that Task 4 is most challenging and interesting. The thinking of doing Task 4 is easy, but I need to fix a lot of problems when doing the matching: As the `city` column of `singer_locations` are not formatted well, i.e. sometimes, it is the full name of the states, sometimes, it's other country/city outside of US, sometimes, it includes some special charactor that could not display in R. As no pattern could be found and no available functions ready, so I have to build up my own functions for the use of `purrr: map()`. In addition, I have to change the output of the file because R indicates that I am using functions that produce HTML output.

When I am doing Task 6 and would like to compare the coef between ls fitting and robust fitting, I found that tidy function does not work for robust method, so I changed the steps of cleaning the data and take a little detour. 

Throughout the whole process of doing the assignment, I searched the website a lot. But finally, I found it is almost impossible to find the specific answers to my specific questions, that could be the way I am describing my questions not clearly. It turned out that the most important source I rely on is R document and package description. 
