---
title: "HW1 Task4"
output: html_document
---

```{r}
library(purrr)
library(repurrrsive)
library(singer)
library(ggmap)
library(leaflet)
library(dplyr)
```


## Task 4: Work With the Singer Data

#### Task 4.1
The singer_location dataframe in the singer package contains geographical information stored in two different formats: 1. as a (dirty!) variable named city; 2. as a latitude / longitude pair (stored in latitude, longitude respectively). The function revgeocode from the ggmap library allows you to retrieve some information for a pair (vector) of longitude, latitude (warning: notice the order in which you need to pass lat and long). Use purrr to map latitude and longitude into human readable information on the band’s origin places. 

```{r results='asis'}
latlng_address <- function(longi, lati, output = "address") {
  revgeocode(c(longi, lati), output = "address")
}
possibly_address <- possibly(latlng_address, "Address not found")

singer_loc_noNA <- 
  singer_locations %>%
  filter(!is.na(latitude), !is.na(longitude)) 

singer_loc <- 
  singer_loc_noNA %>%
  head(25) %>%
  mutate(addr = unlist(
           purrr::map2(longitude, latitude, possibly_address)))

singer_loc_display <- 
  singer_loc %>%
  dplyr::select(city, addr) 
singer_loc_display%>%
  knitr::kable(digits = 2, align ="r", padding = 10)
```

For this question, I firstly built a function that takes two location parameters to calculate the address, and then use `possibly` function to avoid potential errors where the `revgeocode` could not find the place for the given logitude and latitude. Because it takes quite a lot time for the `revgeocode` to find all the locations each run, so I only take the first 25 entries of the singer location data with NA filtered out. Also, for the beaty of display, I choose the most important info to display in the above and following tables.

Not all of the time we make a research through revgeocode() we get a result. What can we do to avoid those errors to bite us? (look at possibly() in purrr…)

#### Task 4.2

Try to check wether the place in city corresponds to the information you retrieved.

```{r, results='asis'}
find_state_abb <- function(city_name){
  state.abb[match(city_name, str_to_lower(state.name))] %>%
    str_to_lower()
}

tokenize <- function(string, trim = FALSE) {
  if (trim) {
    string_trim <- str_trim(sub("^[^,]*,", "", string))
  } else {
    string_trim <- string
  }
  string_split <- unlist(str_split(string_trim, boundary("word")))
  str_to_lower(string_split)
}

city_state_match <- function(address, city) {
  address <- str_to_lower(address)
  city <- str_to_lower(city)
  is_match <- FALSE
  if (str_detect(address, city)) {
    is_match <- TRUE
  } else {
    token_address <- tokenize(address, trim = TRUE)
    token_city <- tokenize(city)
    token_city_state <- find_state_abb(token_city)
    token_city_state <- token_city_state[!is.na(token_city_state)]
    new_token_city <- c(token_city, token_city_state)
    token_match <- intersect(new_token_city, token_address)
    if (length(token_match) != 0) {
      is_match <- TRUE
    }
  }
  is_match
}

singer_loc_full <-
  singer_loc %>% 
  mutate(match_or_not = 
           unlist(map2(addr, city, city_state_match)))

singer_loc_full %>%
  dplyr::select(city, addr, match_or_not) %>%
  knitr::kable(digits = 2, align ="r", padding = 10)
```


#### Task 4.3 Go visual: give a look to the library leaflet and plot some information about the bands. A snippet of code is provided below.
```{r}
cities <- singer_loc_noNA %>%
  dplyr::select(city, latitude, longitude, artist_hotttnesss)

  
leaflet(cities) %>% addTiles() %>%
  addCircles(lng = ~longitude, lat = ~latitude, weight = 1,
    radius = ~artist_hotttnesss * 3000, popup = ~city
  )
```

In the record of Million Song Dataset, more songs are produced in Eastern US than Western US. Also, we can see a lot of blue dots along the coastline of US than in the middle. Could be the reason that artists are highly to be inspired by the sea and beach. 

