---
title: "HW1 Task4"
output: github_document
---

```{r  message=FALSE}
library(purrr)
library(repurrrsive)
library(singer)
library(stringr)
library(ggmap)
library(leaflet)
library(dplyr)
```


## Task 4: Work With the Singer Data

#### Task 4.1

The singer_location dataframe in the singer package contains geographical information stored in two different formats: 1. as a (dirty!) variable named city; 2. as a latitude / longitude pair (stored in latitude, longitude respectively). The function revgeocode from the ggmap library allows you to retrieve some information for a pair (vector) of longitude, latitude (warning: notice the order in which you need to pass lat and long). Use purrr to map latitude and longitude into human readable information on the band’s origin places. 

```{r results='asis', message=FALSE}
latlng_address <- function(longi, lati, output = "address") {
  revgeocode(c(longi, lati), output = "address")
}
possibly_address <- possibly(latlng_address, "Address not found")

singer_loc_noNA <- 
  singer_locations %>%
  filter(!is.na(latitude), !is.na(longitude), !is.na(city)) 

singer_loc <- 
  singer_loc_noNA %>%
  head(25) %>%
  mutate(addr = unlist(
           purrr::map2(longitude, latitude, possibly_address))) %>%
  filter(!is.na(addr))

singer_loc_display <- 
  singer_loc %>%
  head(15)%>%
  dplyr::select(title, artist_name, artist_hotttnesss, city, addr) 
singer_loc_display%>%
  knitr::kable(digits = 2, align ="r", padding = 10)
```

For this question, I firstly built a function that takes two location parameters to calculate the address, and then use `possibly` function to avoid potential errors where the `revgeocode` could not find the place for the given logitude and latitude. Because it takes quite a lot time for the `revgeocode` to find all the locations each run, so I only take the first 25 entries of the singer location data with NA filtered out. Also, for the beaty of display, I choose the most important info to display in the above and following tables.

Not all of the time we make a research through revgeocode() we get a result. What can we do to avoid those errors to bite us? (look at possibly() in purrr…)

#### Task 4.2

Try to check wether the place in city corresponds to the information you retrieved.

```{r, results='asis'}
find_state_abb <- function(city_name){
  state.abb[match(city_name, str_to_lower(state.name))] %>%
    str_to_lower()
}

tokenize <- function(string, trim = FALSE) {
  if (trim) {
    string_trim <- str_trim(sub("^[^,]*,", "", string))
  } else {
    string_trim <- string
  }
  string_split <- unlist(str_split(string_trim, boundary("word")))
  str_to_lower(string_split)
}

city_state_match <- function(address, city) {
  address <- str_to_lower(address)
  city <- str_to_lower(city)
  is_match <- FALSE
  if (str_detect(address, city)) {
    is_match <- TRUE
  } else {
    token_address <- tokenize(address, trim = TRUE)
    token_city <- tokenize(city)
    token_city_state <- find_state_abb(token_city)
    token_city_state <- token_city_state[!is.na(token_city_state)]
    new_token_city <- c(token_city, token_city_state)
    token_match <- intersect(new_token_city, token_address)
    if (length(token_match) != 0) {
      is_match <- TRUE
    }
  }
  is_match
}


singer_loc_full <-
  singer_loc %>% 
  mutate(match_or_not = 
           unlist(map2(addr, city, city_state_match)))

singer_loc_full %>%
  dplyr::select(title, artist_name, city, addr, match_or_not) %>%
  knitr::kable(digits = 2, align ="r", padding = 10)
```

From the above, we can see only 1 city does not match with the address retrieved from `revgeocode`. If we look into that, we can see it is correct the two are not matching. 

#### Task 4.3 Go visual: give a look to the library leaflet and plot some information about the bands. A snippet of code is provided below.
```{r eval=FALSE}
cities <- singer_loc_noNA %>%
  dplyr::select(city, latitude, longitude, artist_hotttnesss)

  
leaflet(cities) %>% addTiles() %>%
  addCircles(lng = ~longitude, lat = ~latitude, weight = 1,
    radius = ~artist_hotttnesss * 3000, popup = ~city
  )
```


![plot](paste(getwd(), "/map_image/", "map2.png", sep = "")
![plot](paste(getwd(), "/map_image/", "map3.png", sep = "")
![plot](paste(getwd(), "/map_image/", "map4.png", sep = "")
![plot](paste(getwd(), "/map_image/", "map5.png", sep = "")
![plot](paste(getwd(), "/map_image/", "map6.png", sep = "")

In the record of Million Song Dataset, more songs are produced in Eastern US than Western US. Also, we can see a lot of blue dots along the coastline of US than in the middle. Could be the reason that artists are highly to be inspired by the sea and beach. 

#### Note:

Due to the function for visualization is only for `HTML_document` output not `github_document` output, so it is easy to show the interactive map here. I have attached serveral pictures so that you could have an idea of what I am talking about. In addition, the html file is also uploaded to my repo, and you can download it to check. 

## Report your process

Among all the questions I tried, I found that Task 4 is most challenging and interesting. The thinking of doing Task 4 is easy, but I need to fix a lot of problems when doing the matching: As the `city` column of `singer_locations` are not formatted well, i.e. sometimes, it is the full name of the states, sometimes, it's other country/city outside of US, sometimes, it includes some special charactor that could not display in R. As no pattern could be found and no available functions ready, so I have to build up my own functions for the use of `purrr: map()`. 

The most frustrating thing when doing this assignment is that `revgeocode` performs not stable for finding some cities based on the latitude and longtitude. Sometimes it could return to a city name, sometimes it fails. When kniting the file, I need to wait for quite a long time because of that. 

#### Go to previous task: [Task 2](https://github.com/zxkathy/STAT547M_Zhao_Xin_HW/blob/master/HW1/Task2/HW01_2.md)

#### Go to next task: [Task 6](https://github.com/zxkathy/STAT547M_Zhao_Xin_HW/blob/master/HW1/Task6/HW01_6.md)


