---
title: "HW1 Task 1"
output: github_document
---

```{r message=FALSE}
library(dplyr)
library(stringr)
```

## Task 1. Character data

#### 14.2.5 Exercises

Q1(a): In code that doesn’t use stringr, you’ll often see paste() and paste0(). What’s the difference between the two functions? 

A1(a): Default value of sep with `paste` function is `sep = " "`, and default value of sep with `paste0` function is `sep = ""`. By default, `paste0` has no separator and output single charactor.

```{r}
paste("a", "b", "c")
paste0("a", "b", "c")
```

From the following example, we can see paste0 can put the strings together and then add the sep element. 

```{r}
paste(rep("student", 4), rep("number", 4), seq(1,4,1), sep = "_", collapse = ", ")
paste0(rep("student", 4), rep("number", 4), seq(1,4,1), sep = "_", collapse = ", ")
```

Q1(b): What stringr function are they equivalent to? 

A1(b): `paste0` and `paste` are equivalent to function of `str_c`.

```{r}
str_c("a", "b", "c")
```


Q1(c): How do the functions differ in their handling of NA?

A1(c): `paste` recognizes `NA` as character element by default, while `str_c` recognizes NA as null element. 

```{r}
x <- c("a", NA, "c")
paste(x)
str_c(x)
str_c(str_replace_na(x))
```

Q2: In your own words, describe the difference between the sep and collapse arguments to str_c().

A2: When your input is several vectors, sep is the what you put in between ith element of vectors, collapse is what you put in betwen new combined new strings, and turn your result into one string.

```{r}
str_c(rep("student", 4), rep("number", 4), seq(1,4,1), sep = "_")
str_c(rep("student", 4), rep("number", 4), seq(1,4,1), sep = "_", collapse = ", ")
```

Q3: Use str_length() and str_sub() to extract the middle character from a string. What will you do if the string has an even number of characters?

A3: I decide to output the middle two characters if the string has an even number of characters. 

```{r}
x <- "abcde"
y <- "abcd"
str_sub(x, (str_length(x)+1)/2, -(str_length(x)+1)/2)
str_sub(y, (str_length(y)+1)/2, -(str_length(y)+1)/2)
```

Q4: What does str_wrap() do? When might you want to use it?

A4: When we have long paragraphs, `str_wrap()` can format them. The way I am using it is as follows. 

```{r}
x <- "This is my test paragraph, and I can write anything here. "
y <- "That is my second test paragraph, and I just want to see what could happen."
cat(str_c(str_wrap(c(x, y), width = 20, indent = 1, exdent = 3), collapse = "\n"))
```

Q5: What does str_trim() do? What’s the opposite of str_trim()?

A5: Trim whitespace of the string, from the direction specified.

```{r}
str_trim("  string", side = "right")
str_trim("  string", side = "left")
```

Q6: Write a function that turns (e.g.) a vector c("a", "b", "c") into the string a, b, and c. Think carefully about what it should do if given a vector of length 0, 1, or 2.
```{r}
x1 <-  c("ab", "cd", "e", "f")
x2 <-  c("ab", "cd", "e")
x3 <-  c("ab")
turn_string <- function(vector) {
  res <- ""
  if (length(vector) < 2){
    res <- str_c(vector)
  }
  else if (length(vector) == 2){
    res <- str_c(vector[1], vector[2], sep = " and ")
  }
  else
  {
    res1 <- str_c(vector[-length(vector)], collapse = ", ")
    res2 <- vector[length(vector)]
    res <- str_c(res1, res2, sep = " and ") 
  }
  cat(res)
}

turn_string(x1)
turn_string(x2)
turn_string(x3)
```


#### 14.3.1.1 Exercises

Q1: Explain why each of these strings don’t match a `\`: `\`, `\\`, `\\\`.

A1: We need to escape `\`, so we need to create regular expression `\\`, because we are using a string, so add two escapes(`\`) before each `\`. 
`\`: escape. 
`\\`: can be also interpreted as `\`.
`\\\`: `\` plus escape, the sentence is not finished.

Q2: How would you match the sequence `"'\`?

A2: We need to add `\\` in front of every normal expressions. 

```{r}
y = "\"\'\\"
writeLines(y)
#str_view(c(y, "abc"), "\\\"\\'\\\\")
```

Q3: What patterns will the regular expression `\..\..\..` match? How would you represent it as a string?

A3: 
```{r}
x = "abc.a.b.c"
y = "\\..\\..\\.."
writeLines(y)
#str_view(c(y, "abc"), "\\\\..\\\\..\\\\..")
```

#### 14.3.2.1 Exercises

1. How would you match the literal string `$^$`?

```{r}
y = "$^$"
writeLines(y)
#str_view(c(y, "abc"), "\\$\\^\\$")
```

#### Note:

As `str_view` function is for `HTML_document` output not `github_document` output, so it is easy to show the results here. But the code will generate the desired results. 

#### Comment:

This is how much I tried, since I am focusing on the following questions, I don't have much time finishing this question. 

#### Go to next task: [Task 2](https://github.com/zxkathy/STAT547M_Zhao_Xin_HW/blob/master/HW1/Task2/HW01_2.md)